### 2024-02-23 documentation/thesis/thesis_document.tex
.

Low-field \gls{mri} systems are predominantly composed of permanent
magnets. Through the connection of these permanent magnets, a consistent
magnetic field of up to \emph{0.35T} can be generated. However, this
achievement comes at the cost of an average system weight of \emph{14t}.
Despite their cost-effectiveness in production and maintenance,
permanent magnets show drawbacks such as high temperature dependence and
used in \gls{mri}s a limited \gls{snr} due to the constrained field
strength. \customcite{NK16}

@@

The temperature stability of the \emph{TLV493D} with a mean value of
20.68\(^{\circ}\)C and a \gls{sd} of
\(\sigma_{t,TLV493D}\)=0.53\(^{\circ}\)C indicates a consistent trend.
This implies a constant tendency. The close grouping of the measured
values around the mean value indicates good stability. The confidence
interval is expected to be between \emph{20.15\(^{\circ}\)C} and
\emph{21.21\(^{\circ}\)C}, which indicates a stable and consistent
temperature measurement. This result is noisier compared to the
temperature stability of the \emph{MMC5603} with stable
\emph{\(\mu_{t, MMC5603NJ}\)=0.53\(^{\circ}\)C} with an accuracy of two
decimal places.

@@

The sensor internal temperature sensors of both tested sensors are
suitable to perform an ambient temperature compensation of measured
values and calibration of the sensor. This is considered in chapter
\emph{Temperature Sensitivity}
\ref{sensor-characterisation-temperature-sensitivity}.

Though it is recommended to use a separate temperature sensor when using
the \emph{TLV493D} or to use a suitable averaging of the temperature and
measured values in order to perform temperature compensation.

@@

In addition, the \gls{dr} for both sensors are measured before the
measurement run to determine the linearity. In this case, this indicates
the minimum and maximum linear measuring range for the selected linear
Hall sensors. A high \gls{dr} enables a more precise detection of
magnetic fields, while a low \gls{dr} can lead to the sensor detecting
magnetic fields outside its detection range \customcite{CSG22}.

@@

>>>>

Low-field \gls{mri} systems are predominantly composed of permanent
magnets. Through the connection of these permanent magnets, a consistent
magnetic field of up to \emph{0.35T} can be generated. However, this
achievement comes at the cost of an average system weight of \emph{14t}.
Despite their cost-effectiveness in production and maintenance,
permanent magnets show drawbacks such as high temperature dependencies.
\customcite{NK16}

@@

The temperature stability of the \emph{TLV493D} with a mean value of
\emph{20.68\(^{\circ}\)C} and a \gls{sd} of
\(\sigma_{t,TLV493D}\)=0.53\(^{\circ}\)C shows a strongly noisy
characteristic with an accuracy of two decimal places. The confidence
interval varies between \emph{20.15\(^{\circ}\)C} and
\emph{21.21\(^{\circ}\)C}, which is In contrast to the \emph{MMC5603}
with stable \emph{19.40\(^{\circ}\)C}, this result is not suitable for
use, e.g.~for temperature compensation. A second measurement run with
another \emph{TLV493D} confirms this result.

@@

As a result, an external temperature sensor should be used for
temperature-critical measurements with the \emph{TLV493D}. This is
considered for the \emph{Temperature Sensitivity} run in chapter
\ref{sensor-characterisation-temperature-sensitivity}.

@@

@@

\hypertarget{dynamic-range-analysis}{%
\subsection{Dynamic Range Analysis}\label{dynamic-range-analysis}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_Sensor_dynamic_range_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
\caption{Sensor dynamic range evaluation results for TLV493D and
MMC5603NJ.
\label{Sensor_dynamic_range_evaluation_results_for_TLV493D_and_MMC5603NJ.png}}
\end{figure}

With the same setup as for the linearity measurement, the \gls{dr} can
be determined outside the range specified by the manufacturer. As a
result, it is possible to analyze how the sensor behaves when the
defined \gls{dr} is exceeded. This allows the extent to which the limits
of the sensors can be exhausted to be taken into account in subsequent
measurement setups. A high \gls{dr} enables a more precise detection of
magnetic fields, while a low \gls{dr} can lead to the sensor detecting
magnetic fields outside its detection range.

Figure
\ref{Sensor_dynamic_range_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
shows the plot of the linearity measurement outside the specified
\gls{dr} for the respective sensor. For the \emph{TLV493D} a \gls{dr} of
almost double the specified \gls{dr} could be measured, with a peak
value of \emph{240mT} with constant linearity deviation. The
\emph{MMC5603NJ} measures the same linear values as in the linearity
measurement. From a measured value of \emph{3.4mT} it reaches a plateau
and does not increase any further. As a result, the full specified
\gls{dr} can be fully utilized with both sensors.

This extended characterized \gls{dr} is not used in the further
analyses. Reference is made exclusively to the values specified by the
manufacturer, as the values determined do not apply to every sensor
\gls{ic} of the same type.
